HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

This section summarises the procedure for annotation involved in computing HUME.
We mark the source sentence as $s$ and the translation sentence as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) human judgements for each semantic unit of $s$,
defined by its UCCA annotation, of whether its meaning has been preserved in $t$.
We note that (1) is performed once for every source sentence, irrespective
of the number of its translations we wish to evaluate.

@@

Since these annotators have to judge the quality of the translation,
they also needed to be fluent in English.\bh{Somewhere we could explain that we
could do a similar annotation with monolinguals, although it entails aligning reference and MT output}

>>>>

This section summarises the procedure for annotation involved in computing HUME.
We mark the source sentence as $s$ and the translation sentence as $t$. 
The procedure involves two manual steps: (1) UCCA-annotating $s$, 
(2) human judgements for each semantic unit of $s$,
defined by its UCCA annotation, of whether its meaning has been preserved in $t$.
We note that (1) is performed once for every source sentence, irrespective
of the number of its translations we wish to evaluate.\footnote{Instead of
relying on the source,
the evaluation could be based on the UCCA structure for the \emph{reference}
translation. This would allow monolingual annotators to take part in the
evaluation. On the downside, the translation would have to be aligned to the
reference and more importantly, we would risk inaccurate judgements due to
the naturally occurring differences between the source and its reference
translations.}

@@

Since these annotators have to judge the quality of the translation,
they also needed to be fluent in English.
% Ondrej did the following in a footnote in Section 3.1 Annotation Procedure
%\bh{Somewhere we could explain that we
%could do a similar annotation with monolinguals, although it entails aligning
%reference and MT output}
